2nd_draft

### 2020-03-17 src/2nd_draft.Rmd
goodness of fit added

```{r}
dummy_municipal<-dummy(assessment_transform$AddressAssessorMunicipalityDesc)
dummy_taxclass<-dummy(assessment_transform$TaxClassCode)
# build x matrix
x<-cbind(dummy_municipal,dummy_taxclass,assessment_transform$AvgTotalAssessmentValue)
y<-assessment_transform$rate
x<-cbind(x,y)
# correct col name
#assessTotal,assessment_aggregate$landTotal,assessment_aggregate$improvementTotal,assessment_aggregate$propertyCount,assessment_aggregate$tax
colnames(x)[26]<-c("AvgTotalAssessmentValue")
colnames(x)[27]<-c("rate")
xm<-x[,1:(ncol(x)-1)]
x.data.frame<-assessment_transform
xm.data.frame<-assessment_transform[,-c(1,8)]
y.data.frame<-assessment_transform$rate
n <- nrow(xm)
k <- 10
ii <- (1:n)%%k + 1
set.seed(123)
N <- 50
mspe.n<-mspe.el<-mspe.la <- mspe.f <- mspe.ri <- mspe.reduced <- rep(0, N)
for (i in 1:N) {
  ii <- sample(ii)
  pr.n<-pr.el<-pr.la <- pr.f <- pr.ri <- pr.reduced <- rep(0, n)
  for (j in 1:k) {
    tmp.ri <- cv.glmnet(x = xm[ii != j, ], y = y[ii != j], lambda = lambdas, 
                        nfolds = 10, alpha = 0, family = "gaussian")
    tmp.la <- cv.glmnet(x = xm[ii != j, ], y = y[ii != j], lambda = lambdas, 
                        nfolds = 10, alpha = 1, family = "gaussian")
    tmp.reduced <- lm(rate ~ factor(TaxClassCode)+factor(AddressAssessorMunicipalityDesc)+AvgTotalAssessmentValue, 
                      data = x.data.frame[ii != j, ])
    tmp.full <- lm(rate ~ factor(AddressAssessorMunicipalityDesc)+factor(TaxClassCode)+assessTotal+landTotal+improvementTotal+propertyCount+AvgTotalAssessmentValue, 
                   data = x.data.frame[ii != j, ])
    # tmp.n<-lm(rate ~ 1, data = x.data.frame[ii != j, ])

@@

    pr.ri[ii == j] <- predict(tmp.ri, s = tmp.ri$lambda.min, newx = xm[ii == 
                                                                         j, ])
    pr.la[ii == j] <- predict(tmp.la, s = tmp.la$lambda.min, newx = xm[ii == 
                                                                         j, ])
    pr.reduced[ii == j] <- predict(tmp.reduced, newdata = x.data.frame[ii == j, ])
    pr.f[ii == j] <- predict(tmp.full, newdata = x.data.frame[ii == j, ])
    # pr.n[ii == j] <- predict(tmp.n, newdata = x.data.frame[ii == j, ])

    index<-which.min(tmp.elastic$results$RMSE)
    pr.el[ii == j] <- predict(tmp.elastic,
                              alpha = tmp.elastic$results[index,1],
                              lambda = tmp.elastic$results[index,2],
                              newdata = xm.data.frame[ii == j, ])
  }
  mspe.ri[i]<-mean((y - pr.ri)^2)
  mspe.la[i]<-mean((y - pr.la)^2)
  mspe.reduced[i]<-mean((y - pr.reduced)^2)
  mspe.f[i]<-mean((y - pr.f)^2)
  # mspe.n[i]<-mean((y - pr.n)^2)
  mspe.el[i]<-mean((y - pr.el)^2)

@@

boxplot(mspe.la, 
        mspe.ri,
        mspe.el, 
        # mspe.n, 
        mspe.reduced, 
        mspe.f, 
        names = c("LASSO", "Ridge", "Elastic Net", "Reduced", "Full"), 
        col = c("steelblue","gray80","pink", "tomato", "springgreen"), 
        cex.axis = 1, 
        cex.lab = 1, 
        cex.main = 2)

>>>>

```{r, warning=FALSE}
dummy_municipal<-dummy(assessment_transform$AddressAssessorMunicipalityDesc)
dummy_taxclass<-dummy(assessment_transform$TaxClassCode)
# build x matrix
x<-cbind(dummy_municipal,dummy_taxclass,assessment_transform$AvgTotalAssessmentValue)
y<-assessment_transform$rate
x<-cbind(x,y)
# correct col name
#assessTotal,assessment_aggregate$landTotal,assessment_aggregate$improvementTotal,assessment_aggregate$propertyCount,assessment_aggregate$tax
colnames(x)[26]<-c("AvgTotalAssessmentValue")
colnames(x)[27]<-c("rate")
xm<-x[,1:(ncol(x)-1)]
x.data.frame<-assessment_transform
xm.data.frame<-assessment_transform[,-c(1,8)]
y.data.frame<-assessment_transform$rate
n <- nrow(xm)
k <- 10
ii <- (1:n)%%k + 1
set.seed(123)
N <- 50
mspe1.n<-mspe1.el<-mspe1.la <- mspe1.f <- mspe1.ri <- mspe1.reduced <- rep(0, N)
mspe.n<-mspe.el<-mspe.la <- mspe.f <- mspe.ri <- mspe.reduced <- rep(0, N)
for (i in 1:N) {
  ii <- sample(ii)
  pr1.n<-pr1.el<-pr1.la <- pr1.f <- pr1.ri <- pr1.reduced <- rep(0, n)
  pr.n<-pr.el<-pr.la <- pr.f <- pr.ri <- pr.reduced <- rep(0, n)
  for (j in 1:k) {
    # ~ models trained!
    tmp.ri <- cv.glmnet(x = xm[ii != j, ], y = y[ii != j], lambda = lambdas, 
                        nfolds = 10, alpha = 0, family = "gaussian")
    tmp.la <- cv.glmnet(x = xm[ii != j, ], y = y[ii != j], lambda = lambdas, 
                        nfolds = 10, alpha = 1, family = "gaussian")
    tmp.reduced <- lm(rate ~ factor(TaxClassCode)+factor(AddressAssessorMunicipalityDesc)+AvgTotalAssessmentValue, 
                      data = x.data.frame[ii != j, ])
    tmp.full <- lm(rate ~ factor(AddressAssessorMunicipalityDesc)+factor(TaxClassCode)+assessTotal+landTotal+improvementTotal+propertyCount+AvgTotalAssessmentValue, 
                   data = x.data.frame[ii != j, ])
    # tmp.n<-lm(rate ~ 1, data = x.data.frame[ii != j, ])

@@

    # ~ prediction vector on train set
    pr1.ri[ii != j] <- predict(tmp.ri, s = tmp.ri$lambda.min, newx = xm[ii !=
                                                                         j, ])
    pr1.la[ii != j] <- predict(tmp.la, s = tmp.la$lambda.min, newx = xm[ii !=
                                                                         j, ])
    pr1.reduced[ii != j] <- predict(tmp.reduced, newdata = x.data.frame[ii != j, ])
    pr1.f[ii != j] <- predict(tmp.full, newdata = x.data.frame[ii != j, ])
    # pr1.n[ii != j] <- predict(tmp.n, newdata = x.data.frame[ii != j, ])

    # index<-which.min(tmp.elastic$results$RMSE)
    # pr1.el[ii != j] <- predict(tmp.elastic,
    #                           alpha = tmp.elastic$results[index,1],
    #                           lambda = tmp.elastic$results[index,2],
    #                           newdata = xm.data.frame[ii == j, ])

    # ~ prediction vector on test set
    pr.ri[ii == j] <- predict(tmp.ri, s = tmp.ri$lambda.min, newx = xm[ii == 
                                                                         j, ])
    pr.la[ii == j] <- predict(tmp.la, s = tmp.la$lambda.min, newx = xm[ii == 
                                                                         j, ])
    pr.reduced[ii == j] <- predict(tmp.reduced, newdata = x.data.frame[ii == j, ])
    pr.f[ii == j] <- predict(tmp.full, newdata = x.data.frame[ii == j, ])
    # pr.n[ii == j] <- predict(tmp.n, newdata = x.data.frame[ii == j, ])
    # index<-which.min(tmp.elastic$results$RMSE)
    # pr.el[ii == j] <- predict(tmp.elastic,
    #                           alpha = tmp.elastic$results[index,1],
    #                           lambda = tmp.elastic$results[index,2],
    #                           newdata = xm.data.frame[ii == j, ])
  }

  # goodness of fit
  mspe1.ri[i]<-mean((y - pr1.ri)^2)
  mspe1.la[i]<-mean((y - pr1.la)^2)
  mspe1.reduced[i]<-mean((y - pr1.reduced)^2)
  mspe1.f[i]<-mean((y - pr1.f)^2)
  # mspe1.n[i]<-mean((y - pr1.n)^2)
  # mspe1.el[i]<-mean((y - pr1.el)^2)

  # prediction power
  mspe.ri[i]<-mean((y - pr.ri)^2)
  mspe.la[i]<-mean((y - pr.la)^2)
  mspe.reduced[i]<-mean((y - pr.reduced)^2)
  mspe.f[i]<-mean((y - pr.f)^2)
  # mspe.n[i]<-mean((y - pr.n)^2)
  # mspe.el[i]<-mean((y - pr.el)^2)

@@

boxplot(mspe1.la, 
        mspe1.ri,
        # mspe1.el, 
        # mspe1.n, 
        mspe1.reduced, 
        mspe1.f, 
        names = c("LASSO", 
                  "Ridge", 
                  # "Elastic Net", 
                  "Reduced", 
                  "Full"), 
        col = c("steelblue","gray80",
                # "pink", 
                "tomato", "springgreen"), 
        cex.axis = 1, 
        cex.lab = 1, 
        cex.main = 2,
        main = "Goodness of Fit",
        ylab = "MSE")

boxplot(mspe.la, 
        mspe.ri,
        # mspe.el, 
        # mspe.n, 
        mspe.reduced, 
        mspe.f, 
        names = c("LASSO", "Ridge", 
                  # "Elastic Net", 
                  "Reduced", "Full"), 
        col = c("steelblue","gray80",
                # "pink", 
                "tomato", "springgreen"), 
        cex.axis = 1, 
        cex.lab = 1, 
        cex.main = 2,
        main = "Prediction Power",
        ylab = "MSPE")
